### 2021-12-16 documentos/generators.tex
Párrafo de caracterización de PCEgs. Falta prueba para N qubits

In this section we will discuss the existence of a generator set for all PCE
quantum channels, how to label each element of this set according to its local-action to 
every qubit in the system, and, finally, we  	will discuss a symmetry of
both PCE quantum channel generators and $A$, the matrix that diagonalizes
the Choi matrix $\mcD_N$ of a PCE map.

@@

%\cpnote{Arreglar}
\janote{Discutir con Carlos}
PCE generators may be characterized by its local-action on every qubit 
in the system, and thus be denoted as $\mcG_{\vec\alpha}$. First, let us denote
the four 1-qubit PCE generators as $\mcG_{\alpha}$, with $\alpha=0,1,2,3$.
The first being the trivial generator and the remaining the channels that 
map the Bloch sphere to each of the Cartesian axes.
%PCE generator may be identified with a unique vector index
%$\vec\alpha$, and thus be denoted as $\pceg$.
% El numero de generadores concide con esa vaina. 
%Let us introduce a convention for the following discussion for 
%the indices in $\vec\alpha$; the number 0 to 3 identifies
%Recall that indices $0,1,2,3$ in $\vec\alpha$ correspond to, respectively,
%the identity map and the 3 1-qubit PCE quantum channels that project the 
%Bloch sphere to the rectangular axes $x$, $y$ and $z$. 
%If one sets all indices in $\vec\alpha$ to zero except for the $k$-th index.
\janote{A rigorous explanation of why every $\vec\alpha$ is corresponded
to every generator.}
Therefore we can identify the index $\alpha_k$ in $\vec\alpha$ with the local-action
of the PCE generator on the $k$-th qubit. In consequence, we will denote 
PCE generators as $\mcG_{\vec\alpha}$. 
See in \Fref{fig:appex:twoQ_PCEGs} the notation of  two-qubit PCE generators.
%See, for example, non-trivial generators in subfigures (c), (d) and (e) of
%\Fref{fig:examplesPCE} are denoted $\mcG_{(1,3)}$, $\mcG_{(3,2)}$ and
%$\mcG_{(2,2)}$, respectively.
%whose local-action on the first qubit (first column) is to project the corresponding local Bloch sphere 
%to the $x$ axis and on the second qubit (first row) to map the corresponding
%local Bloch sphere to itself, may be characterized with the vector index (1,0). 
%Then, it is clear that in general one can associate a unique $\vec\alpha$ to 
%every PCE generator and so denote them as $\pceg$.

@@

>>>>

In this section we will discuss the existence of a generator set for all PCE
quantum channels, how to label each of them uniquely according to its local-action 
on every qubit in the system, and, finally, we  	will discuss a symmetry of
both PCE quantum channel generators and $A$, the matrix that diagonalizes
the Choi matrix $\mcD_N$ of a PCE map.

@@

%\cpnote{Arreglar}
PCE generators may be characterized by its local-action on every qubit 
in the system, and thus each of them be denoted as $\mcG_{\vec\alpha}$, 
with $\vec\alpha$ each of the $4^{n}$ different vector indices. For 1-qubit
the PCE generators are the identity map plus the channels that map the Bloch 
sphere to each Cartesian axis, as their associated vector subspaces are trivial
to prove and their dimension 1 is met. 
\janote{Here goes the bla bla for the discussion of the proof for the $N$-qubit
\pce{} generators}
Therefore we can identify the index $\alpha_k$ in $\vec\alpha$ with the local-action
of the PCE generator on the $k$-th qubit. In consequence, we will denote 
PCE generators as $\mcG_{\vec\alpha}$. 
See, for example, that the 2-qubits PCE generator represented in subfigure (c)
in \Fref{fig:two:qubit:examples} acts on the first qubit (first column) as mapping its
Bloch sphere to de $x$-axis, and on the second qubit (first row) acts an identity,
hence it is labeled $\mcG_{(1,0)}$.
See \Fref{fig:appex:twoQ_PCEGs} for the notation of all 2-qubit PCE generators.

@@

\begin{align}
\tau_{(\vec\alpha)}
\end{align}
